---
title: "Homework 5"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
  fig.width = 9,
  fig.asp = .8,
  out.width = "90%"
)
theme_set(theme_bw() + theme(legend.position = "bottom"))
```

## Problem 1

### Import and tidy data

Create a tidy dataframe containing data from all participants:

First, start with a dataframe containing all file names and read in data:

```{r load_data, message = FALSE}
longitudinal_df = 
  tibble(file_names = list.files("./data/")) %>% 
  mutate(subject_data = map(str_c("./data/", file_names), read_csv))
```

Then, tidy the dataset:

```{r tidy_data}
longitudinal_tidy = 
  longitudinal_df %>% 
  unnest %>% 
  mutate(file_names = str_replace(file_names, ".csv", "")) %>% 
  separate(file_names, into = c("arm", "subject_ID"), sep = "_") %>% 
  mutate(arm = str_replace(arm, "con", "control"),
         arm = str_replace(arm, "exp", "experimental")) %>% 
  gather(key = week, value = observation, week_1:week_8) %>% 
  mutate(week = str_replace(week, "week_", ""),
         week = as.integer(week)) %>% 
  arrange(arm, subject_ID)
```

Look at the resulting dataset:

```{r check_result}
longitudinal_tidy
str(longitudinal_tidy)
```

### Spaghetti plot

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups:

```{r spaghetti_plot}
longitudinal_tidy %>% 
  mutate(ID = str_c(arm, "_", subject_ID)) %>% 
  ggplot(aes(x = week, y = observation, group = ID, color = arm)) + 
    geom_line() + 
    labs(
      title = "Observations on each subject over time",
      x = "Week",
      y = "Observation",
      caption = "Data from the longitudinal study"
    ) 
```

From the sphaghetti plot, the experimental group and control group had similar observations at baseline. However, the observations of subjects in experimental group are generally higher than observations of subjects in control group through 8 weeks. The difference between two groups increased over time since subjects assigned to the experimental arm had increasing observation values across weeks while subjects assigned to the control arm had relatively constant observation values.

I find this plot is clearer for comparing observations between groups than two-panel plot with each individual having different colors.

## Problem 2

### Import data

First, load and describe the row data:

```{r load_homicide, message = FALSE}
homicide_df = read_csv("./homicide-data.csv")
homicide_df
```

The Washington Post homicide dataset contains `r nrow(homicide_df)` observations, where each observation is a case of homicide.

There are 12 variables in this dataset:  

uid: homicide identifier;  
reported_date: the date on which the killing was reported;  
victim_last: the last name of the victim;  
victim_first: the first name of the victim;  
victim_race: the race of the victim;  
victim_age: the age of the victim;  
victim_sex: the sex of the victim;  
city, state, lat, lon:  the location of the killing;  
disposition: whether the case was closed and whether an arrest was made.

### Number of total and unsolved homicides

Create a city_state variable and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides:

```{r summarize_city}
homicide_city_state = 
  homicide_df %>%  
  mutate(city_state = str_c(city, ",", state)) 

homicide_number = 
  homicide_city_state %>% 
  group_by(city_state) %>%
  summarise(n_total = n(), 
            n_unsolved = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))) %>% 
  filter(!(n_unsolved == 0))
homicide_number
```

I created a dataset called homicide_city_state containing a city_state variable, and then group by city_state and summarise to obtain the resulting dataframe.

For the city of Baltimore, MD:

First, estimate the proportion of homicides that are unsolved.

```{r estimate_Baltimore}
baltimore_data = 
  homicide_number %>% 
  filter(city_state == "Baltimore,MD") 
prop.test(baltimore_data$n_unsolved, baltimore_data$n_total)
```

Then, save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r prop_ci_baltimore}
baltimore_prop_tidy = 
  prop.test(baltimore_data$n_unsolved, baltimore_data$n_total) %>% 
  broom::tidy() %>% 
  janitor::clean_names()
baltimore_prop_tidy

baltimore_prop_tidy %>% 
  select(estimate, conf_low, conf_high) %>% 
  rename(Estimate = estimate, 
         "Lower limit" = conf_low, 
         "Upper limit" = conf_high) %>% 
  knitr::kable()
```

From the resulting dataframe and the above table, the estimated proportion of homicides that are unsolved in Baltimore is 0.646, and the 95% confidence interval is (0.628, 0.663).

Create a tidy dataframe with estimated proportions of unsolved homicides and CIs for each city:

```{r prop_ci_cities}
prop_tidy = function(df){
  prop_test = prop.test(df$n_unsolved, df$n_total)
  broom::tidy(prop_test)
}

city_state_nest = nest(homicide_number, n_total:n_unsolved)

prop_ci = 
  city_state_nest %>% 
  mutate(prop_unsolved = map(data, prop_tidy)) %>% 
  unnest() %>% 
  janitor::clean_names() %>% 
  select(city_state, estimate, conf_low, conf_high)
prop_ci
```

I wrote a function called prop_tidy that runs prop.test for each of the cities, saves the result to an object called prop_test and then applys the broom::tidy to this object. I created a dataframe containing a list column. Then I used map to iterate over the list column and finally created a tidy dataframe with estimated proportions and CIs for each city.

### Errorbar plot

Create a plot that shows the estimates and CIs for each city:

```{r errorbar}
prop_ci %>% 
  mutate(city_state = fct_reorder(city_state, desc(estimate))) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) +
  theme(axis.text.x = element_text(angle = 80, hjust = 1)) +
  labs(title = "Estimated proportion and 95% CI of unsolved cases in 50 large US cities", 
       y = "Proportion of unsolved cases", 
       x = "City and State", 
       caption = "Data from the Washington Post") 
```

The above plot shows the estimate and 95% CI of proportion of unsolved homicides for each city, ordered from most to least. Chicago has the highest proportion of unsolved cases, while Richmond has the lowest proportion of unsolved cases. 